Project-I by Group MexicoCity

### 2014-11-02 report/paper.tex
up3

We checked the correlation between output and input variables. The correlation matrix helped us to discover which variables where correlated to no other variables nor the output. We could remove these variables.\textcolor{red}{More details to add here :youssef text}
\section{Least Squares}
Applying the least squares method on the data without cleaning yields a $RMSE$ of $0.48244$.
\section{Best method : Ridge Regression}
\textcolor{red}{explain what is the best method and why for our dataset, add some figures and results}
\section{Feature transformations}
\textcolor{red}{Different transformation (myPoly, sqrt, etc)}
\section{Summary}
\textcolor{red}{summarize in a few lines and write down all the final results}

>>>>

We checked the correlation between output and input variables. The correlation matrix helped us to discover which variables where correlated to no other variables nor the output. We could remove these variables.
\section{Least Squares}
The mean gives a $RMSE$ of 0.99964, over normalized $\mathbf{y}$.\\

Applying the least squares method on the data without cleaning yields a $RMSE$ of $0.48244$. Given that, we see that the $RMSE$ is cut by half so the input data are meaningful.
\section{Ridge Regression}
\textcolor{red}{explain what is the best method and why for our dataset, add some figures and results}\\

By visually inspecting the Pearson correlation graphs, a good strategy to spot well correlated input variables was to take the intersection of the two methods (we’re only considering ). To do that, we tried multiplying the two coefficients (for each variable) and taking the mean. Both strategies clearly showed the 18th and 34th variables are best correlated. We can limit our variable transform to these two (we only have 1400 data points, so with a dimension 48 we’re already lacking data, by introducing spurious transforms we would be adding fuel to the fire and causing overfitting.)
\section{Logistic Regression}
We tried to use simple logistic regression using all the variable, the estimated $RMSE$ test error was 0.27099. Also we tried using sqrt on the 11th and 24th variables which actually improves our test error to 0.26779. We can also use squares of the variables instead of the square root and applying this alone the test error decreased to 0.26715. Adding both transformations got us a decrease to a test error of 0.26474. We also tried to remove all categorical variables as we did in regression, but the test error increased to 0.3396, so their information was needed and cannot be ignored.

We then found that, since Pearson correlation predicted better correlation of square roots than squares but squares were actually better able to decrease test error, it might be a good idea to include 3rd degree transforms of the 11th and 24th variables. Added them, the test error increased to 0.26656. Thus taking higher orders doesn’t seem to help.

\textcolor{red}{to section transformation?}We then tried to include a dummy variable transform, but that increased the test error significantly to 0.32625, therefore we’re not going to use them.
\section{Feature transformations}
\textcolor{red}{Different transformation (myPoly, sqrt, etc)}
\section{Summary}
\textcolor{red}{summarize in a few lines and write down all the final results}
